Large integer arithmetic and polynomial inner product

### 2012-11-11 doc/paper_vli/vli.tex
doc typo

To conclude, we developed an optional hybrid mode between CPU/GPU, this  technic is usual in GPU computing \cite{CUDAReduction}. We split the inputs vectors of polynomials into two chucks of datas, execute concurrently on CPU and GPU. Only at the end, a synchronization during  the memory transfer is done  for the final reduction.

@@

Evaluate  integer benchmarks integer are not easy, contrary to float number, it does not exist a universal\footnote{Altough the MIPS exists (Million Instructions Per Seconds), it should be the equivalent of the FLOPS, it's signification is disputable} value as the FLOPS for floating-point operation, because integer operations performed by ALU, and the number of  ALU is not constant between processor, and the execution of the operation are not constant.  We compute the  result  numbers as GOP/s$=10^{-9} \times batch/t$, where  $batch$ is the number of long integer operations computed during the execution (additions and multiplications), $t$ [s]  is the elapsed time, we note the execution time for GPU contains the memory  transfer.

>>>>

To conclude, we developed an optional hybrid mode between CPU/GPU, this  technic is usual in GPU computing \cite{magma}. We split the inputs vectors of polynomials into two chucks of datas, execute concurrently on CPU and GPU. Only at the end, a synchronization during  the memory transfer is done  for the final reduction.

@@

Evaluate  integer benchmarks integer are not easy, contrary to float number, it does not exist a universal\footnote{Altough the MIPS exists (Million Instructions Per Seconds), it should be the equivalent of the FLOPS, it's signification is disputable} value as the FLOPS for floating-point operation, because integer operations performed by ALU, and the number of  ALU is not constant between processor, and the execution of the operation are not constant \cite{ASMcost}.  We compute the  result  numbers as GOP/s$=10^{-9} \times batch/t$, where  $batch$ is the number of long integer operations computed during the execution (additions and multiplications), $t$ [s]  is the elapsed time, we note the execution time for GPU contains the memory  transfer.
